Compositional equivalences based on Open pNets

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
ajout related work; cond transi

There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g. DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.  The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach. A formal comparison would be interesting, though not trivial. What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules. Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.  Last, we intentionaly do not accept negative premisses, that would be more diffcult to put into practice in our implementation. an extension could be studied in future work.

\subsubsection*{Symbolic and data-sensitive systems}
 As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al. \cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}. They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes. Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e. congruent), even for the weak version. This result is more general than the bisimulation congruences for value-passing CCS in \cite{IngolfsdottirL:2001}. Then our settings for management of data types are much less restrictive, thanks to our use of satisfiability engines, while Lin's algorithms were limited to data-independent systems.

>>>>

Among the approaches for modelling open systems, where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}. Our formalism open automata is different from both, in that they are parametrised models.

There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g. DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.  The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach. A formal comparison would be interesting, though not trivial. What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules. Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.  Last, we intentionally do not accept negative premisses, that would be more  to put into practice in our implementation. an extension could be studied in future work.

\subsubsection*{Symbolic and data-sensitive systems}
 As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al. \cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}. They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes. Our work extends these in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e. congruent), even for the weak version. This result is more general than the bisimulation congruences for value-passing CCS in \cite{IngolfsdottirL:2001}. Then our settings for management of data types are much less restrictive, thanks to our use of satisfiability engines, while Lin's algorithms were limited to data-independent systems.
